An event-sourced and distributed database with IPLD and materialized views

### 2019-09-20 draft.tex

\begin{definition}
(Raw). This variant declares that consumers are not expected to make additional assumptions. This is the default variant. 
\end{definition}

Example (V1, 128 bit): `bafkxd5bjgi6k4zivuoyxo4ua4mzyy`

\begin{definition}
(Access-Controlled): This variant declares that consumers should assume an access control list is composable from Log Events. The ACL represents a permissions rule set that must be applied when reading data (see Section  \ref{sec:AccessControl}).
\end{definition}

Example (V1, 256 bit): `bafyoiobghzefwlidfrwkqmzz2ka66zgmdmgeobw2mimktr5jivsavya`

>>>>

\begin{definition}
(Raw). This variant declares that consumers are not expected to make additional assumptions. This is the default variant.\\

See Example \ref{ex:Identity}).
\end{definition}

\begin{definition}
(Access-Controlled): This variant declares that consumers should assume an access control list is composable from Log Events. The ACL represents a permissions rule set that must be applied when reading data (see Section  \ref{sec:AccessControl}).\\

See Example \ref{ex:Identity}).
\end{definition}

\begin{example*}
\centering
\begin{minipage}{0.6\textwidth}
\begin{lstlisting}[language=json,firstnumber=1]
# Raw identity. V1, 128 bit
bafkxd5bjgi6k4zivuoyxo4ua4mzyy

# ACL enabled identity. V1, 256 bit.
bafyoiobghzefwlidfrwkqmzz2ka66zgmdmgeobw2mimktr5jivsavya
\end{lstlisting}
\end{minipage}
  \caption{Identity variants.}
  \label{ex:Identity}
\end{example*}
